Universal Anonymous Signatures

### 2022-05-05 prism-backend/research/gsac/app-gsac.tex
Making a pass.

        \procedure{$\OBTISS(\uid,\cid,\Attrs)$}{%
          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cred, \utrans \rangle \gets
          \langle \Obtain(\gpk,\PRVUK[\uid],\Attrs), \\
          \pcind \pcind \pcind \pcind \pcind \pcind
          \Issue(\gpk,\isk,\Attrs) \rangle \\
          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets (\uid,\cred,\Attrs) \\
          \pcreturn \top \\
        }

        \procedure{$\OBTAIN(\uid,\cid,\Attrs)$}{%
          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\gpk,\PRVUK[\uid],\Attrs),\adv \rangle \\
          \CRED[\cid] \gets (\uid,\cred,\Attrs) \\
          \pcreturn \top \\
        }

@@

        \procedure{$\ISSUE(\uid,\cid,\Attrs)$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, \Issue(\gpk,\isk,\Attrs) \rangle \\
          \trans[\cid] \gets \utrans;~
          \CRED[\cid] \gets (\uid,\cdot,\Attrs) \\
          \pcreturn \top \\          
        }

        \procedure{$\SIGN(\cid,\DAttrs,\msg)$}{%
          \uid \gets \OWNR[\cid] \\
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \cred \gets \CRED[\cid] \\
          \sig \gets \Sign(\gpk,\PRVUK[\uid],\cred,\DAttrs,\msg) \\
          \SIG[\cid] \gets \SIG[\cid] \cup \lbrace (\sig,\DAttrs,\msg) \rbrace \\
          \pcreturn \sig \\
        }

        \procedure{$\OPEN(\sig)$}{%
          \textrm{Let}~\cid~\textrm{be s.t.}~(\sig,\DAttrs,\msg) \in \SIG[\cid] \\
          \pcif \textrm{no such \cid exists, or there is more than one}: \\
          \pcind \pcreturn \bot \\
          \pcif \sig \in \CSIG: \pcreturn \bot \\
          (\upk,\oproof) \gets \Open(\gpk,\osk,\sig,\DAttrs,\msg) \\
%          \OSIG \gets \OSIG \cup \lbrace (\sig,\upk,\cred) \rbrace \\
%          \CCRED \gets \CCRED \cup \lbrace \cid \rbrace \\
          \pcreturn (\upk,\oproof) \\
        }

        \procedure{$\CHALb(\ccid_0,\ccid_1,\DAttrs,\msg)$}{%
          \pcif \DAttrs \nsubseteq \ATTR[\ccid_0] \cap \ATTR[\ccid_1]:
          \pcreturn \bot \\
          \pcif \cuid_0 \neq \bot \lor \cuid_1 \neq \bot: \pcreturn \bot \\
          \cuid_0 = \OWNR[\ccid_0];~\cuid_1 = \OWNR[\ccid_1] \\
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
 %         \pcif \ccid_0 \in \CCRED \lor \ccid_1 \in \CCRED: \pcreturn \bot \\
          \csig \gets \Sign(\gpk,\PRVUK[\cuid_b],\CRED[\ccid_b],
          \DAttrs,\msg) \\
          \CSIG \gets \CSIG \cup \lbrace \csig \rbrace \\
          \pcreturn \csig
        }

@@

  \begin{description}
  \item[$O$.] The \Open algorithm returns $\bot$.
  \item[$J$.] The \Judge algorithm returns $0$.
  \item[$D$.] No credential owned by a user in \CU contains \DAttrs.
  \end{description}

@@

  \begin{description}
  \item[$W_1 = O$.] \Open returns $\bot$ (line 5 of \ExpGSACTrace).
  \item[$W_2 = \overline{O} \land J$.] \Open does not fail, but \Judge rejects
    the output of \Open (line 7 of \ExpGSACTrace).
  \item[$W_3 = \overline{O} \land \overline{J} \land D$.] \Open does not fail,
    \Judge accepts the output by \Open, but no corrupt user has a credential
    containing \DAttrs (line 8 of \ExpGSACTrace).
  \end{description}

  Clearly, since the group signature is verified at step 4 of the game, if
  verification succeeds, soundness of $\NIZK_{\Sign}$ implies that $(\Ccom_m,
  \Ec,\DAttrs) \in \NIZKLang_{\Sign}$, except with negligible probability
  $2^{-\NIZKsecpar}$. Also, observe that each of the winning events for the
  adversary described above are disjoint. Thus:

@@

  $\Pr[W_1]=0$ is directly deduced from the fact that $(\Ccom_m,\Ec,\DAttrs)
  \in \NIZKLang_{\Sign}$ due to soundness of $\NIZKRel_{\Sign}$. Concretely,
  we know that \Open does not abort due to rejection of the signature by
  \Verify (as this is checked in line 4 of \ExpGSACTrace too) and, thus,
  $\Ec = \EEnc(\opk,\Ccom)$ which, by correctness of the encryption algorithm,
  implies that $\Ccom = \EDec(\osk,\Ec)$, where $\upk=\Ccom=\CCommit(\usk;0)$.
  Completeness of $\NIZK_{\Open}$ thus implies that the \Open algorithm can
  compute the opening proof \oproof, and return $(\upk,\oproof)$.

@@

  Finally, assume that there is an adversary $\adv$ against \ExpGSACTrace that
  wins by event $W_3$. Then, it is straight forward to build an adversary \advB
  against unforgeability of the signature scheme on blocks of committed
  messages. Namely, \advB creates the parameters with \Setup and the opening
  key pair with \OKeyGen, but instead of running \IKeyGen, sets the verification
  key to the one received in the \ExpSBCMOMF game. In calls by $\adv$ to \OBTISS
  and \ISSUE oracles, \advB replaces the \Issue algorithm with corresponding
  calls to its $\langle \cdot,\SBCMSign \rangle$ oracle. The other oracles are
  unchanged. Without loss of generality, suppose that $\adv$ makes a total of
  $n$ queries to \OBTISS and \ISSUE, combined; which implies that \advB makes
  a total of $n$ queries to its own oracle. If, in such an execution, $\adv$
  wins by event $W_3$, it means that it has produced a signature \sig, revealing
  attribute set \DAttrs, that is accepted by \Verify, for which \Open does not
  fail, and for which an honestly generated open proof is accepted by \Judge,
  but such that no issued credential contains \DAttrs. Soundness of
  $\NIZK_{\Sign}$ implies that \sig is a valid signature over $\Attrs \cup
  \lbrace \usk \rbrace$, and $\DAttrs \subseteq \Attrs$; but \sig has not been
  produced via a call to the $\langle \cdot,\SBCMSign \rangle$ oracle. Thus,
  \advB can output at least $n+1$ valid signatures, which contradicts security
  of \SBCM.
  %
  By assumption of security of \SBCM, $\Pr[W_3]$ must therefore be negligible in
  $\SBCMsecpar$ and, consequently: $\AdvGSACTrace(\secpar) = \negl(\SBCMsecpar)+
  \negl(\NIZKsecpar)$, which is negligible.  
  \qed
\end{proof}

@@

  Finally, assume that $\adv$ wins \ExpGSACNonframe with non-negligible
  probability. This means that it outputs a $(\sig = (\Ec,\pi_\sig),\DAttrs,
  \msg,\upk,\pi)$, where $(\sig,\DAttrs,\msg)$ are accepted by \Verify, and
  $(\upk,\pi,\sig,\DAttrs,\msg)$ are accepted by \Judge. Thus, after soundness
  of $\NIZK^{\NIZKRel_{\Sign}}$ and $\NIZK^{\NIZKRel_{\Open}}$, we know that
  \upk is the correct public key associated to an honest user \uid, but as per
  the winning condition, \sig has not been produced via a call to the \SIGN
  oracle for a \cid owned by \uid. Therefore, we can extract the \usk
  corresponding to \upk from the $\pi_{\sig}$ proof. Since executions in the
  environment prepared by \advB are indistinguishable to $\adv$ from executions
  of $G_0$, we can assume that the probability that the \uid associated to the
  \sig output by $\adv$ equals $1/q$. In that case, \usk precisely matches
  $\msg_b$, and \advB wins the hiding game against \C. Since we assume \C
  to be hiding, this probability must therefore be negligible.   
  \qed
\end{proof}

@@

Intuitively, the credentials that we generate for our \GSAC construction are
Pedersen commitments to $(\usk,\credid,\Attrs)$ tuples; i.e., they have
the following structure: $\gen{h}_0^r\gen{h}_1^{\usk}\prod_{i \in [2,\nattrs+1]}
\gen{h}_i^{\Attrs_i}$, where the exponent in $\gen{h_0}$ is a fresh random value
that ensures hiding, the exponent in $\gen{h_1}$ encodes the user private
key, and the remaining attributes are encoded in different
exponentiations. This will actually be part of a BBS+ signature, which makes it
easy to add subsequent and efficient zero-knowledge proofs. Concretely, we will
be using several \NIZK proof systems, one for the $\langle \Obtain,\Issue
\rangle$ interactive protocol, another for signing, and a third one for opening.
Each will have its own relation, that we define in the corresponding algorithm.
The concrete algorithms are as follows.

@@

\paragraph{$\langle \Obtain(\gpk,\usk,\Attrs),\Issue(\gpk,\isk,\Attrs) \rangle
  \rightarrow \langle \cred/\bot,\utrans/\bot \rangle$.} %
This interactive protocol is essentially a BBS+ signing  process. The user
commits to its private key, proves knowledge of the corresponding private
key, and asks the issuer to sign the commitment, along with any other arbitraty
set of revealed attributes \Attrs. For proving knowledge of the private key, we
define relation $\NIZKRel_{\Issue} = \lbrace (r, \usk), \Ccom: \Ccom =
\gen{h}_0^r\gen{h}_1^{\usk}\rbrace$.

\begin{itemize}
\item \underline{User}: Fetch fresh randomness $r \getr \ZZ^*_p,
  \Ccom \gets \gen{h}_0^r\gen{h}_1^{\usk}$, and compute $\NIZKproof \gets
  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs,(r,\usk),
  \Ccom)$. Send $(\Ccom,\NIZKproof)$ to Issuer.
\item \underline{Issuer}: Run $\NIZKVerify^{\NIZKRel_{\Issue}}(\NIZKcrs,\Ccom,
  \NIZKproof)$ and return $0$ if it fails. Else, compute
  $x,\tilde{s} \getr \ZZ^*_p, A \gets
  (\gen{g}_1\Ccom h_0^{\tilde{s}} \prod_{i \in \Attrs}
  \gen{h}_i^{\Attrs_i})^{1/(\isk+x)}$.
  Send $(A,x,\tilde{s})$ to User, and output $\utrans \gets
  (\Ccom,(A,x,\tilde{s}),\Attrs,\NIZKproof)$.
\item \underline{User}: If $A = 1_{\GG_1}$: return $0$. Else, compute
  $s \gets r + \tilde{s}$. If $e(A,\gen{g}_2)^xe(A,\ipk) \neq
  e(\gen{g}_1\Ccom\gen{h}_0^{\tilde{s}}\prod_{i \in \Attrs}\gen{h}_i^{\Attrs_i},
  \gen{g}_2)$: return $0$. Else, return
  $(A,x,s)$.
\end{itemize}

\paragraph{$\Sign(\gpk,\usk,\cred,\DAttrs,\msg) \rightarrow \sig$.} %
To create a signature, the user first randomizes its BBS+ credential \cred and
encrypts its public key \upk (note that $\upk=\gen{h}_1^{\usk}$ with the
opener's encryption key. Then, we extend the usual NIZK protocol for proving
knowledge of BBS+ signatures \cite{cdl16b} to, in addition to proving knowledge
of a signature (which, for us is the user credential), also prove that the
attribute encoding \usk within the credential match the encrypted value.
Finally, the user commits to \msg, and includes this commitment within the
proof. For this, we define relation
$\NIZKRel_{\Sign}= \lbrace (r,\usk,\Attrs,r_2,r_3,s',\msg),(\DAttrs,c_1,c_2,
\Cmsg): \Cmsg = \gen{h}^\msg \land c_1 = g^r \land c_2 = \opk^r\gen{h}_1^{\usk}
\land \hat{A}/d = (A')^{-x}\gen{h}_0^{r_2} \land
\gen{g}_1 \prod_{i \in \DAttrs} \gen{h}_i^{\Attrs_i} =
d^{r_3}\gen{h}_0^{-s'}\gen{h}_1^{-\usk}
\prod_{i \notin \DAttrs} \gen{h}_i^{-\Attrs_i} \rbrace$.

\begin{itemize}
\item Parse \gpk as $(\ipk,\opk)$, and \cred as $(A,x,s)$.
\item Re-randomize \cred as $r_1,r_2 \getr
  \ZZ^*_p, r_3 \gets r_1^{-1}, s' \gets s - r_2r_3$, $A' \gets A^{r_1},
  \hat{A} \gets (A')^{-x}(\gen{g}_1\gen{h}_0^s\gen{h}_1^{\usk}
  \prod_{i \in \Attrs}\gen{h}_i^{\Attrs_i})^{r_1}$,
  $d \gets (\gen{g}_1\gen{h}_0^s\gen{h}_1^{\usk}
  \prod_{i \in \Attrs}\gen{h}_i^{\Attrs_i})^{r_1}\gen{h}_0^{-r_2}$.
\item Encrypt $\upk=\gen{h}_1^{\usk}$ with ElGamal as $r \getr \ZZ^*_p,
  c \gets (c_1 = \gen{g}^r,c_2 = \opk^r\gen{h}_1^{\usk})$.
\item Compute $\Cmsg \gets \gen{h}^\msg$ and
  $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs,
  (r,\usk,\Attrs,r_2,r_3,s',\msg), (\DAttrs,c_1,c_2,\Cmsg))$.
\item Return $\sig \gets (c=(c_1,c_2),(A',\hat{A},d),\NIZKproof)$.
\end{itemize}

\paragraph{$\Verify(\gpk,\sig,\DAttrs,\msg) \rightarrow 1/0$.} %
Parse \gpk as $(\ipk,\opk)$ and $\sig$ as $(c=(c_1,c_2),
(A',\hat{A},d), \NIZKproof)$. Check that $A' \neq 1_{\GG_1}$ and $e(A',\ipk) =
e(\hat{A},\gen{g}_2)$. Compute $\Cmsg \gets \gen{h}^\msg,$ and return
$\NIZKVerify^{\NIZKRel_{\Sign}}(\NIZKcrs,(\DAttrs,c_1,c_2,\Cmsg),
\NIZKproof)$.

\paragraph{$\Open(\gpk,\osk,\sig,\DAttrs,\msg)
  \rightarrow (\upk,\oproof)/\bot$.} %
For open algorithms, we define the following relation for correct decryption of
ElGamal ciphertexts: $\NIZKRel_{\Open} = \lbrace \osk,(c_1,c_2,\msg):
c_2/c_1^{\osk} = \msg \rbrace$. Given $\NIZKRel_{\Open}$, the opener first,
checks that $\Verify$ accepts the signature, and aborts otherwise. If \sig
is accepted, then parses \sig as $(c=(c_1,c_2),\cdot,\cdot)$.
Sets $\upk \gets c_2/c_1^{\osk}$. Finally, computes the proof of correct
decryption by running $\oproof \gets \NIZKProve^{\NIZKRel_{\Open}}(\NIZKcrs,
\osk,(\upk,c_1,c_2))$, and returns $(\upk,\oproof)$.

\paragraph{$\Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg)
  \rightarrow 1/0$.} %
First, check that $\Verify$ accepts \sig, and abort otherwise. If the signature
is accepted, then parse \sig as $(c=(c_1,c_2),\cdot,\cdot)$ and return
$\NIZKVerify^{\NIZKRel_{\Open}}(\NIZKcrs,(c_1,c_2,\upk),\oproof)$.

% \commentwho{Jesus}{For consistency with \UAS, maybe remove the need to return
%   \Attrs in \Open, and return \DAttrs instead. Then, we do not need to pass
%   \trans as a parameter to \Open, as \DAttrs is already attested for in the
%   signature being opened. It also makes sense from the point of view that we
%   are already revealing \upk, which would allow tracing; but otherwise don't
%   reveal anything else about the attributes of \upk -- attributes that whoever
%   requested the signature (the verifier) didn't seem to consider necessary, as
%   s/he only requested \DAttrs. Still, if we make this modification, mention the
%   possibility to return \Attrs, and the option to do it via adding \trans as a
%   parameter to \Open (or including an encryption of all attributes in the
%   signature, which is probably unrealistic.)}

>>>>

        \procedure{$\OBTISS(\uid,\cid,\attrs)$}{%
          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cred, \utrans \rangle \gets
          \langle \Obtain(\gpk,\PRVUK[\uid],\attrs), \\
          \pcind \pcind \pcind \pcind \pcind \pcind
          \Issue(\gpk,\isk,\attrs) \rangle \\
          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets (\uid,\cred,\attrs) \\
          \pcreturn \top \\
        }

        \procedure{$\OBTAIN(\uid,\cid,\attrs)$}{%
          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\gpk,\PRVUK[\uid],\attrs),\adv \rangle \\
          \CRED[\cid] \gets (\uid,\cred,\attrs) \\
          \pcreturn \top \\
        }

@@

        \procedure{$\ISSUE(\uid,\cid,\attrs)$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, \Issue(\gpk,\isk,\attrs) \rangle \\
          \trans[\cid] \gets \utrans;~
          \CRED[\cid] \gets (\uid,\cdot,\attrs) \\
          \pcreturn \top \\          
        }

        \procedure{$\SIGN(\cid,\dattrs,\msg)$}{%
          \uid \gets \OWNR[\cid] \\
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \cred \gets \CRED[\cid] \\
          \sig \gets \Sign(\gpk,\PRVUK[\uid],\cred,\dattrs,\msg) \\
          \SIG[\cid] \gets \SIG[\cid] \cup \lbrace (\sig,\dattrs,\msg) \rbrace \\
          \pcreturn \sig \\
        }

        \procedure{$\OPEN(\sig)$}{%
          \textrm{Let}~\cid~\textrm{be s.t.}~(\sig,\dattrs,\msg) \in \SIG[\cid] \\
          \pcif \textrm{no such \cid exists, or there is more than one}: \\
          \pcind \pcreturn \bot \\
          \pcif \sig \in \CSIG: \pcreturn \bot \\
          (\upk,\oproof) \gets \Open(\gpk,\osk,\sig,\dattrs,\msg) \\
%          \OSIG \gets \OSIG \cup \lbrace (\sig,\upk,\cred) \rbrace \\
%          \CCRED \gets \CCRED \cup \lbrace \cid \rbrace \\
          \pcreturn (\upk,\oproof) \\
        }

        \procedure{$\CHALb(\ccid_0,\ccid_1,\dattrs,\msg)$}{%
          \pcif \dattrs \nsubseteq \ATTR[\ccid_0] \cap \ATTR[\ccid_1]:
          \pcreturn \bot \\
          \pcif \cuid_0 \neq \bot \lor \cuid_1 \neq \bot: \pcreturn \bot \\
          \cuid_0 = \OWNR[\ccid_0];~\cuid_1 = \OWNR[\ccid_1] \\
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
 %         \pcif \ccid_0 \in \CCRED \lor \ccid_1 \in \CCRED: \pcreturn \bot \\
          \csig \gets \Sign(\gpk,\PRVUK[\cuid_b],\CRED[\ccid_b],
          \dattrs,\msg) \\
          \CSIG \gets \CSIG \cup \lbrace \csig \rbrace \\
          \pcreturn \csig
        }

@@

  \begin{description}
  \item[$O$.] The \Open algorithm returns $\bot$.
  \item[$J$.] The \Judge algorithm returns $0$.
  \item[$D$.] No credential owned by a user in \CU contains \dattrs.
  \end{description}

@@

  \begin{description}
  \item[$W_1 = O$.] \Open returns $\bot$ (line 5 of \ExpGSACTrace).
  \item[$W_2 = \overline{O} \land J$.] \Open does not fail, but \Judge rejects
    the output of \Open (line 7 of \ExpGSACTrace).
  \item[$W_3 = \overline{O} \land \overline{J} \land D$.] \Open does not fail,
    \Judge accepts the output by \Open, but no corrupt user has a credential
    containing \dattrs (line 8 of \ExpGSACTrace).
  \end{description}

  Clearly, since the group signature is verified at step 4 of the game, if
  verification succeeds, soundness of $\NIZK_{\Sign}$ implies that $(\Ccom_m,
  \Ec,\dattrs) \in \NIZKLang_{\Sign}$, except with negligible probability
  $2^{-\NIZKsecpar}$. Also, observe that each of the winning events for the
  adversary described above are disjoint. Thus:

@@

  $\Pr[W_1]=0$ is directly deduced from the fact that $(\Ccom_m,\Ec,\dattrs)
  \in \NIZKLang_{\Sign}$ due to soundness of $\NIZKRel_{\Sign}$. Concretely,
  we know that \Open does not abort due to rejection of the signature by
  \Verify (as this is checked in line 4 of \ExpGSACTrace too) and, thus,
  $\Ec = \EEnc(\opk,\Ccom)$ which, by correctness of the encryption algorithm,
  implies that $\Ccom = \EDec(\osk,\Ec)$, where $\upk=\Ccom=\CCommit(\usk;0)$.
  Completeness of $\NIZK_{\Open}$ thus implies that the \Open algorithm can
  compute the opening proof \oproof, and return $(\upk,\oproof)$.

@@

  Finally, assume that there is an adversary $\adv$ against \ExpGSACTrace that
  wins by event $W_3$. Then, it is straight forward to build an adversary \advB
  against unforgeability of the signature scheme on blocks of committed
  messages. Namely, \advB creates the parameters with \Setup and the opening
  key pair with \OKeyGen, but instead of running \IKeyGen, sets the verification
  key to the one received in the \ExpSBCMOMF game. In calls by $\adv$ to \OBTISS
  and \ISSUE oracles, \advB replaces the \Issue algorithm with corresponding
  calls to its $\langle \cdot,\SBCMSign \rangle$ oracle. The other oracles are
  unchanged. Without loss of generality, suppose that $\adv$ makes a total of
  $n$ queries to \OBTISS and \ISSUE, combined; which implies that \advB makes
  a total of $n$ queries to its own oracle. If, in such an execution, $\adv$
  wins by event $W_3$, it means that it has produced a signature \sig, revealing
  attribute set \dattrs, that is accepted by \Verify, for which \Open does not
  fail, and for which an honestly generated open proof is accepted by \Judge,
  but such that no issued credential contains \dattrs. Soundness of
  $\NIZK_{\Sign}$ implies that \sig is a valid signature over $\attrs \cup
  \lbrace \usk \rbrace$, and $\dattrs \subseteq \attrs$; but \sig has not been
  produced via a call to the $\langle \cdot,\SBCMSign \rangle$ oracle. Thus,
  \advB can output at least $n+1$ valid signatures, which contradicts security
  of \SBCM.
  %
  By assumption of security of \SBCM, $\Pr[W_3]$ must therefore be negligible in
  $\SBCMsecpar$ and, consequently: $\AdvGSACTrace(\secpar) = \negl(\SBCMsecpar)+
  \negl(\NIZKsecpar)$, which is negligible.  
  \qed
\end{proof}

@@

  Finally, assume that $\adv$ wins \ExpGSACNonframe with non-negligible
  probability. This means that it outputs a $(\sig = (\Ec,\pi_\sig),\dattrs,
  \msg,\upk,\pi)$, where $(\sig,\dattrs,\msg)$ are accepted by \Verify, and
  $(\upk,\pi,\sig,\dattrs,\msg)$ are accepted by \Judge. Thus, after soundness
  of $\NIZK^{\NIZKRel_{\Sign}}$ and $\NIZK^{\NIZKRel_{\Open}}$, we know that
  \upk is the correct public key associated to an honest user \uid, but as per
  the winning condition, \sig has not been produced via a call to the \SIGN
  oracle for a \cid owned by \uid. Therefore, we can extract the \usk
  corresponding to \upk from the $\pi_{\sig}$ proof. Since executions in the
  environment prepared by \advB are indistinguishable to $\adv$ from executions
  of $G_0$, we can assume that the probability that the \uid associated to the
  \sig output by $\adv$ equals $1/q$. In that case, \usk precisely matches
  $\msg_b$, and \advB wins the hiding game against \C. Since we assume \C
  to be hiding, this probability must therefore be negligible.   
  \qed
\end{proof}

@@

Intuitively, the credentials that we generate for our \GSAC construction are
Pedersen commitments to $(\usk,\credid,\attrs)$ tuples; i.e., they have
the following structure: $\gen{h}_0^r\gen{h}_1^{\usk}\prod_{i \in [2,\nattrs+1]}
\gen{h}_i^{\attrs_i}$, where the exponent in $\gen{h_0}$ is a fresh random value
that ensures hiding, the exponent in $\gen{h_1}$ encodes the user private
key, and the remaining attributes are encoded in different
exponentiations. This will actually be part of a BBS+ signature, which makes it
easy to add subsequent and efficient zero-knowledge proofs. Concretely, we will
be using several \NIZK proof systems, one for the $\langle \Obtain,\Issue
\rangle$ interactive protocol, another for signing, and a third one for opening.
Each will have its own relation, that we define in the corresponding algorithm.
The concrete algorithms are as follows.

@@

\paragraph{$\langle \Obtain(\gpk,\usk,\attrs),\Issue(\gpk,\isk,\attrs) \rangle
  \rightarrow \langle \cred/\bot,\utrans/\bot \rangle$.} %
This interactive protocol is essentially a BBS+ signing  process. The user
commits to its private key, proves knowledge of the corresponding private
key, and asks the issuer to sign the commitment, along with any other arbitraty
set of revealed attributes \attrs. For proving knowledge of the private key, we
define relation $\NIZKRel_{\Issue} = \lbrace (r, \usk), \Ccom: \Ccom =
\gen{h}_0^r\gen{h}_1^{\usk}\rbrace$.

\begin{itemize}
\item \underline{User}: Fetch fresh randomness $r \getr \ZZ^*_p,
  \Ccom \gets \gen{h}_0^r\gen{h}_1^{\usk}$, and compute $\NIZKproof \gets
  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs,(r,\usk),
  \Ccom)$. Send $(\Ccom,\NIZKproof)$ to Issuer.
\item \underline{Issuer}: Run $\NIZKVerify^{\NIZKRel_{\Issue}}(\NIZKcrs,\Ccom,
  \NIZKproof)$ and return $0$ if it fails. Else, compute
  $x,\tilde{s} \getr \ZZ^*_p, A \gets
  (\gen{g}_1\Ccom h_0^{\tilde{s}} \prod_{i \in \attrs}
  \gen{h}_i^{\attrs_i})^{1/(\isk+x)}$.
  Send $(A,x,\tilde{s})$ to User, and output $\utrans \gets
  (\Ccom,(A,x,\tilde{s}),\attrs,\NIZKproof)$.
\item \underline{User}: If $A = 1_{\GG_1}$: return $0$. Else, compute
  $s \gets r + \tilde{s}$. If $e(A,\gen{g}_2)^xe(A,\ipk) \neq
  e(\gen{g}_1\Ccom\gen{h}_0^{\tilde{s}}\prod_{i \in \attrs}\gen{h}_i^{\attrs_i},
  \gen{g}_2)$: return $0$. Else, return
  $(A,x,s)$.
\end{itemize}

\paragraph{$\Sign(\gpk,\usk,\cred,\dattrs,\msg) \rightarrow \sig$.} %
To create a signature, the user first randomizes its BBS+ credential \cred and
encrypts its public key \upk (note that $\upk=\gen{h}_1^{\usk}$ with the
opener's encryption key. Then, we extend the usual NIZK protocol for proving
knowledge of BBS+ signatures \cite{cdl16b} to, in addition to proving knowledge
of a signature (which, for us is the user credential), also prove that the
attribute encoding \usk within the credential match the encrypted value.
Finally, the user commits to \msg, and includes this commitment within the
proof. For this, we define relation
$\NIZKRel_{\Sign}= \lbrace (r,\usk,\attrs,r_2,r_3,s',\msg),(\dattrs,c_1,c_2,
\Cmsg): \Cmsg = \gen{h}^\msg \land c_1 = g^r \land c_2 = \opk^r\gen{h}_1^{\usk}
\land \hat{A}/d = (A')^{-x}\gen{h}_0^{r_2} \land
\gen{g}_1 \prod_{i \in \dattrs} \gen{h}_i^{\attrs_i} =
d^{r_3}\gen{h}_0^{-s'}\gen{h}_1^{-\usk}
\prod_{i \notin \dattrs} \gen{h}_i^{-\attrs_i} \rbrace$.

\begin{itemize}
\item Parse \gpk as $(\ipk,\opk)$, and \cred as $(A,x,s)$.
\item Re-randomize \cred as $r_1,r_2 \getr
  \ZZ^*_p, r_3 \gets r_1^{-1}, s' \gets s - r_2r_3$, $A' \gets A^{r_1},
  \hat{A} \gets (A')^{-x}(\gen{g}_1\gen{h}_0^s\gen{h}_1^{\usk}
  \prod_{i \in \attrs}\gen{h}_i^{\attrs_i})^{r_1}$,
  $d \gets (\gen{g}_1\gen{h}_0^s\gen{h}_1^{\usk}
  \prod_{i \in \attrs}\gen{h}_i^{\attrs_i})^{r_1}\gen{h}_0^{-r_2}$.
\item Encrypt $\upk=\gen{h}_1^{\usk}$ with ElGamal as $r \getr \ZZ^*_p,
  c \gets (c_1 = \gen{g}^r,c_2 = \opk^r\gen{h}_1^{\usk})$.
\item Compute $\Cmsg \gets \gen{h}^\msg$ and
  $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs,
  (r,\usk,\attrs,r_2,r_3,s',\msg), (\dattrs,c_1,c_2,\Cmsg))$.
\item Return $\sig \gets (c=(c_1,c_2),(A',\hat{A},d),\NIZKproof)$.
\end{itemize}

\paragraph{$\Verify(\gpk,\sig,\dattrs,\msg) \rightarrow 1/0$.} %
Parse \gpk as $(\ipk,\opk)$ and $\sig$ as $(c=(c_1,c_2),
(A',\hat{A},d), \NIZKproof)$. Check that $A' \neq 1_{\GG_1}$ and $e(A',\ipk) =
e(\hat{A},\gen{g}_2)$. Compute $\Cmsg \gets \gen{h}^\msg,$ and return
$\NIZKVerify^{\NIZKRel_{\Sign}}(\NIZKcrs,(\dattrs,c_1,c_2,\Cmsg),
\NIZKproof)$.

\paragraph{$\Open(\gpk,\osk,\sig,\dattrs,\msg)
  \rightarrow (\upk,\oproof)/\bot$.} %
For open algorithms, we define the following relation for correct decryption of
ElGamal ciphertexts: $\NIZKRel_{\Open} = \lbrace \osk,(c_1,c_2,\msg):
c_2/c_1^{\osk} = \msg \rbrace$. Given $\NIZKRel_{\Open}$, the opener first,
checks that $\Verify$ accepts the signature, and aborts otherwise. If \sig
is accepted, then parses \sig as $(c=(c_1,c_2),\cdot,\cdot)$.
Sets $\upk \gets c_2/c_1^{\osk}$. Finally, computes the proof of correct
decryption by running $\oproof \gets \NIZKProve^{\NIZKRel_{\Open}}(\NIZKcrs,
\osk,(\upk,c_1,c_2))$, and returns $(\upk,\oproof)$.

\paragraph{$\Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg)
  \rightarrow 1/0$.} %
First, check that $\Verify$ accepts \sig, and abort otherwise. If the signature
is accepted, then parse \sig as $(c=(c_1,c_2),\cdot,\cdot)$ and return
$\NIZKVerify^{\NIZKRel_{\Open}}(\NIZKcrs,(c_1,c_2,\upk),\oproof)$.

% \commentwho{Jesus}{For consistency with \UAS, maybe remove the need to return
%   \attrs in \Open, and return \dattrs instead. Then, we do not need to pass
%   \trans as a parameter to \Open, as \dattrs is already attested for in the
%   signature being opened. It also makes sense from the point of view that we
%   are already revealing \upk, which would allow tracing; but otherwise don't
%   reveal anything else about the attributes of \upk -- attributes that whoever
%   requested the signature (the verifier) didn't seem to consider necessary, as
%   s/he only requested \dattrs. Still, if we make this modification, mention the
%   possibility to return \attrs, and the option to do it via adding \trans as a
%   parameter to \Open (or including an encryption of all attributes in the
%   signature, which is probably unrealistic.)}

### 2022-05-05 prism-backend/research/gsac/conclusion.tex
Merged GSAC and UAS into uas.tex paper. Defining concrete instantiation of GSAC.
Making a pass.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "sok-privsig"
%%% End:

>>>>

Some notes on future work, to expand/refine/remove:

\begin{itemize}
\item Add support for open functions over sets of previously issued signatures.
  This would cover existing schemes like \cite{dl21}, and possibly cool cases
  such as training AI models on private data, in a federated manner, without
  revealing the identity of the node running the model.
\item Currently, in \UAS, we need to restrict challenge users to present
  credentials issued by the same set of issuers. Technically, I guess that this
  could be done by making the issuers' public keys part of the witness (although,
  at what cost?). But then, how would verifiers be able to determine whether
  they trust the issuers of the credentials used to compute the signature? It
  would be as if an employer has to accept a University degree, without knowing
  which university issued it.  
\item Potentially very cool improvement in the modelling: maybe we can leverage
  a decentralized append-only bulletin board (so, a blockchain) to reduce trust
  on the issuers (except identity proofing, we could probably eliminate it...)
  That would be quite innovative, as in GS literature, the issuer has so far
  alwasy been thought to be necessarily honest. (Disclaimer: this was Ezequiel's
  suggestion!)
\item The current syntax of \UAS does not seem to support blind issuance. This
  would however be trivial to achieve by adding a set of attributes to be
  blindly issued in the \Obtain algorithm, and then requiring that they are
  validated in \fissue. In the generic construction, this would be directly
  supported too, as a block of messages to be signed as part of the block
  commitment.
\end{itemize}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas"
%%% End:
